Liptschiz

### 2024-02-23 lipschitz/valabstraction.tex
update another group of constraints

\vspace*{-11ex}

@@

\vspace*{-10ex}

@@

The following two plots show its shape:

>>>>

@@

@@

A more direct way to establish the constraints is as follows: \begin{align*}
	& x_i \leq a\beta_i \quad\wedge \quad x_i\geq (1-a)\alpha_i\\	
	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
	&\hat{y}_i \leq -(a+a')\gamma_i \quad\wedge \quad	\hat{y}_i \geq (a+a')\gamma_i \\
	&	\hat{y}_i \leq y_i+(2-a-a')\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (2-a-a')\gamma_i \\
	&	\hat{y}_i \leq -x_i+(1+a-a')\beta_i \quad\wedge \quad	\hat{y}_i \geq -x_i+(1+a-a')\alpha_i \\
	&	\hat{y}_i \leq y_i+x_i+(1+a'-a)\beta_i \quad\wedge \quad	\hat{y}_i \geq y_i+x_i+(1+a'-a)\alpha_i \\
\end{align*}The following two plots show its shape:
